Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-10 ms.tex
writing conclusions about comparison of dust SED emission models

\subsection{Single-MBB versus Two-component emission}
In both the correlation slope analysis of $\S$\ref{sec:global} and the 
goodness-of-fit analysis of $\S$\ref{sec:hier} we found that the 
best-fit \PLANCK+DIRBE two-component model (Table \ref{tab:global}, model 2) 
outperformed the best-fit single-MBB model, but by a lesser margin than found 
by FDS99 using FIRAS+DIRBE. We found $\Delta \chi^2_{nu}$= and $\Delta$

>>>>

\subsection{Single-MBB versus Two-component emission}
% could use an opening sentence here just reiterating that a major thrust of
% this work was to decide whether the two-component model
% still makes sense after swapping in Planck for FIRAS

% second sentence of opening paragraph reiterating what the basic two
% strategies were that we employed to compare dust SED models

In both the correlation slope analysis of $\S$\ref{sec:global} and the 
goodness-of-fit analysis of $\S$\ref{sec:hier} we found that the 
best-fit \PLANCK+DIRBE two-component model (Table \ref{tab:global}, model 2) 
outperformed the best-fit single-MBB model, but by a lesser margin than found 
by FDS99 using FIRAS+DIRBE. Specifically, our best-fit \PLANCK+DIRBE 
two-component model yielded an improvement of $\Delta \chi^2_{\nu}$=3.41 
($\S$\ref{sec:global}) and $\Delta \chi^2_{\nu}$=0.4 ($\S$\ref{sec:hier}). This
represents a far less dramatic contrast than found by the FDS99 correlation 
slope analysis, $\Delta \chi^2_{\nu}$=29.2. Perhaps, though, the relative lack 
of discrimination amongst competing dust SED models when relying on 
\PLANCK+DIRBE is not surprising, given that our constraints include only nine 
broad frequency channels, whereas FDS99 employed $>$200 narrow bands.
